\documentclass[article]

\begin{document}

\title{Lab 0: Average speed, uncertainty, and error bars}

When you're driving along the highway, your car's spedometer tells you
the speed at a given time. Other times, you might care more about how
long it takes you to make the whole trip, with statements like ``I
live 10 minutes away from the University.'' Suppose you were on a
bicycle and wanted to know how much longer it would take you to get
somewhere based on how fast you were currently going. How could you
estimate that? Does it depend on whether or not your speed stays
constant the whole time?

\section{Equipment}
\begin{itemize}
\item Motorized toy car
\item Meter stick
\item Stopwatch
\end{itemize}

\section{Prediction}

Do you expect a toy car to move with constant velocity? If you perform
repeated trials with increasing distance, how should the total transit
time per trial change?

\section{Warm up questions}
\begin{itemize}

\item What does constant velocity motion look like? If the toy car
  moves with roughly constant velocity, what do you expect to see?

\item If the toy car moves with constant velocity, how can you 

\end{itemize}


\section{Exploration}

How well does the cart travel across the floor? Do you notice any
apparent changes in velocity? 

How quickly can you start and stop the stopwatch? When the cart
crosses a finish line, how hard is it to tell when it has crossed?
Decide on a way to estimate the uncertainty of your measurements.

\section{Procedure}

Mark a distance on the floor and time the cart travelling from start
to finish. What was the velocity? 

How far does the cart have to travel before you can reliably measure
the time it takes? Decide on several distances at which you plan to
make a measurement, and measure the time it takes the toy car to
travel them. What are the uncertainties (appendix B)?

\section{Analysis}

Plot the times and distances for each of the trials using error bars
(appendix C). 

\section{Conclusion}

How do you interpret the plot you just made? How can you tell whether
or not the car travelled at a roughly constant velocity during this
experiment?




